A Large-Scale Study of the Use of Eval in R

### 2020-08-23 inst/paper/main.tex
Add basic eval numbers

@@

In our corpus eval is called \missingNumber times out of \missingNumber
total calls to all R functions. This is merely \missingPercentage of the total
number of calls. \missingTable breaks down the number of calls and callsites for
the four kinds of eval functions from the three source; core R, packages and
Kaggle code.

>>>>

\input{counts.tex}

@@

In our corpus eval is called \AllAllCallCountRnd{} times out of \missingNumber
total calls to all R functions. This is merely \missingPercentage of the total
number of calls. \missingTable breaks down the number of calls and callsites for
the four kinds of eval functions from the three source; core R, packages and
Kaggle code.

\begin{tabular}{c|c|c|c|c|c}
  Corpus  & eval & evalq & evalParent & local & all \\
  Core & \CoreEvalCallCountRnd & \CoreEvalqCallCountRnd & \CoreEvalParentCallCountRnd & \CoreLocalCallCountRnd & \CoreAllCallCountRnd \\
  Package & \PackageEvalCallCountRnd & \PackageEvalqCallCount & \PackageEvalParentCallCountRnd & \PackageLocalCallCountRnd & \PackageAllCallCountRnd \\
\end{tabular}
